Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-21 paper.Rmd
initial hookup with daily flights

```{r}
###Preparatory codes

@@

@@

fb <- open_sky %>% transmute(ADEP = origin, ADES = destination, TYPE = as.factor(typecode), DATE = date(day), CALL = callsign, ACFT_ID = aircraft_uid)

>>>>

```{r globalstuff, message=FALSE}
## set bookdown specs/defaults for high quality output
#---------- check for the settings

## theme default for ggplot
theme_set(
  theme_minimal()
  )

###Preparatory codes

@@

This study builds on publicly available data. Opensky Network collects crowdsourced air traffic data from more than 2500 feeders (sensor stations). To support the process of illustrating and studying the impact of the COVID pandemic on air traffic demand, a flight-by-flight dataset is provided on a monthly basis [@xavier_olive_2021_4893103]. The data spans the period since 1. January 2019. Fig. \@ref(fig:osndaily) shows the number of daily flights tracked by Opensky Network globally.

<!-- add some data set description, e.g. number of files, etc -->

(ref:osndaily) Daily flights tracked by Opensky Network

```{r osndaily, fig.cap="(ref:osndaily)", message=FALSE}
daily_tfc <- read_csv("./data/daily_osn.csv")

daily_tfc %>%
  ggplot(mapping = aes(x = DATE, y = FLTS)) +
  geom_line() +
  labs(x = NULL, y = "flights")
```

@@

fb <- open_sky %>% transmute(ADEP = origin, ADES = destination, TYPE = as.factor(typecode), DATE = date(day), CALL = callsign
                             #, ACFT_ID = aircraft_uid
                             )
